Generating a README.txt file for the Dryad submission of data from study "DateLife: leveraging databases and analytical tools to reveal the dated Tree of Life

### 2022-07-18 dryad/README.Rmd
updating dryad readme with cross validation files

```{r}
line2 <- "DATA & FILE OVERVIEW

@@

File 12 Name: Sanchez-Reyes_etal_2022_supplementary_figure_S1.pdf    
File 12 Description: PDf file showing results of cross validation analysis of datelife's chronogram generating functions.

File 13 Name: Sanchez-Reyes_etal_2022_supplementary_figure_S2.jpg    
File 13 Description: JPG file of results of cross validation analysis of datelife's chronogram generating functions, using a tree topology from Barker et al. 2013. Comparison of original chronogram (black) and the chronogram obtained using datelife (gray).

File 14 Name: Sanchez-Reyes_etal_2022_supplementary_figure_S2.tre    
File 14 Description: Newick file of chronogram obtained with datelife, shown in supplementary Figure S2 (gray).

File 15 Name: Sanchez-Reyes_etal_2022_supplementary_figure_S3.jpg    
File 15 Description: JPG file of results of cross validation analysis of datelife's chronogram generating functions, using a tree topology from Barker et al. 2015, chronogram 1. Comparison of original chronogram (black) and the chronogram obtained using datelife (gray).

File 16 Name: Sanchez-Reyes_etal_2022_supplementary_figure_S3.tre    
File 16 Description: Newick file of chronogram obtained with datelife, shown in supplementary Figure S3 (gray).

File 17 Name: Sanchez-Reyes_etal_2022_supplementary_figure_S4.jpg    
File 17 Description: JPG file of results of cross validation analysis of datelife's chronogram generating functions, using a tree topology from Barker et al. 2015, chronogram 2. Comparison of original chronogram (black) and the chronogram obtained using datelife (gray).

File 18 Name: Sanchez-Reyes_etal_2022_supplementary_figure_S4.tre    
File 18 Description: Newick file of chronogram obtained with datelife, shown in supplementary Figure S4 (gray).

File 19 Name: Sanchez-Reyes_etal_2022_supplementary_figure_S5.jpg    
File 19 Description: JPG file of results of cross validation analysis of datelife's chronogram generating functions, using a tree topology from Burns et al. 2015. Comparison of original chronogram (black) and the chronogram obtained using datelife (gray).

File 20 Name: Sanchez-Reyes_etal_2022_supplementary_figure_S5.tre    
File 20 Description: Newick file of chronogram obtained with datelife, shown in supplementary Figure S5 (gray).

File 21 Name: Sanchez-Reyes_etal_2022_supplementary_figure_S6.jpg    
File 21 Description: JPG file of results of cross validation analysis of datelife's chronogram generating functions, using a tree topology from Claramunt et al. 2015. Comparison of original chronogram (black) and the chronogram obtained using datelife (gray).

File 22 Name: Sanchez-Reyes_etal_2022_supplementary_figure_S6.tre    
File 22 Description: Newick file of chronogram obtained with datelife, shown in supplementary Figure S6 (gray).

File 23 Name: Sanchez-Reyes_etal_2022_supplementary_figure_S7.jpg    
File 23 Description: JPG file of results of cross validation analysis of datelife's chronogram generating functions, using a tree topology from Gibb et al. 2015. Comparison of original chronogram (black) and the chronogram obtained using datelife (gray).

File 24 Name: Sanchez-Reyes_etal_2022_supplementary_figure_S7.tre    
File 24 Description: Newick file of chronogram obtained with datelife, shown in supplementary Figure S7 (gray).

File 25 Name: Sanchez-Reyes_etal_2022_supplementary_figure_S8.jpg    
File 25 Description: JPG file of results of cross validation analysis of datelife's chronogram generating functions, using a tree topology from Hedges et al. 2015, chronogram 1. Comparison of original chronogram (black) and the chronogram obtained using datelife (gray).

File 26 Name: Sanchez-Reyes_etal_2022_supplementary_figure_S8.tre    
File 26 Description: Newick file of chronogram obtained with datelife, shown in supplementary Figure S8 (gray).

File 27 Name: Sanchez-Reyes_etal_2022_supplementary_figure_S9.jpg    
File 27 Description: JPG file of results of cross validation analysis of datelife's chronogram generating functions, using a tree topology from Hedges et al. 2015, chronogram 2. Comparison of original chronogram (black) and the chronogram obtained using datelife (gray).

File 28 Name: Sanchez-Reyes_etal_2022_supplementary_figure_S9.tre    
File 28 Description: Newick file of chronogram obtained with datelife, shown in supplementary Figure S9 (gray).

File 29 Name: Sanchez-Reyes_etal_2022_supplementary_figure_S10.jpg    
File 29 Description: JPG file of results of cross validation analysis of datelife's chronogram generating functions, using a tree topology from Hooper et al. 2017. Comparison of original chronogram (black) and the chronogram obtained using datelife (gray).

File 30 Name: Sanchez-Reyes_etal_2022_supplementary_figure_S10.tre    
File 30 Description: Newick file of chronogram obtained with datelife, shown in supplementary Figure S10 (gray).

File 31 Name: Sanchez-Reyes_etal_2022_supplementary_figure_S11.jpg    
File 31 Description: JPG file of results of cross validation analysis of datelife's chronogram generating functions, using a tree topology from Jetz et al. 2012, chronogram 1. Comparison of original chronogram (black) and the chronogram obtained using datelife (gray).

File 32 Name: Sanchez-Reyes_etal_2022_supplementary_figure_S11.tre    
File 32 Description: Newick file of chronogram obtained with datelife, shown in supplementary Figure S11 (gray).

File 33 Name: Sanchez-Reyes_etal_2022_supplementary_figure_S12.jpg    
File 33 Description: JPG file of results of cross validation analysis of datelife's chronogram generating functions, using a tree topology from Jetz et al. 2012, chronogram 2. Comparison of original chronogram (black) and the chronogram obtained using datelife (gray).

File 34 Name: Sanchez-Reyes_etal_2022_supplementary_figure_S12.tre    
File 34 Description: Newick file of chronogram obtained with datelife, shown in supplementary Figure S12 (gray).

File 35 Name: Sanchez-Reyes_etal_2022_supplementary_figure_S13.jpg    
File 35 Description: JPG file of results of cross validation analysis of datelife's chronogram generating functions, using a tree topology from Kimball et al. 2019, chronogram 1. Comparison of original chronogram (black) and the chronogram obtained using datelife (gray).

File 36 Name: Sanchez-Reyes_etal_2022_supplementary_figure_S13.tre    
File 36 Description: Newick file of chronogram obtained with datelife, shown in supplementary Figure S13 (gray).

File 37 Name: Sanchez-Reyes_etal_2022_supplementary_figure_S14.jpg    
File 37 Description: JPG file of results of cross validation analysis of datelife's chronogram generating functions, using a tree topology from Kimball et al. 2019, chronogram 2. Comparison of original chronogram (black) and the chronogram obtained using datelife (gray).

File 38 Name: Sanchez-Reyes_etal_2022_supplementary_figure_S14.tre    
File 38 Description: Newick file of chronogram obtained with datelife, shown in supplementary Figure S14 (gray).

File 39 Name: Sanchez-Reyes_etal_2022_supplementary_figure_S15.jpg    
File 39 Description: JPG file of results of cross validation analysis of datelife's chronogram generating functions, using a tree topology from Oliveros et al. 2019. Comparison of original chronogram (black) and the chronogram obtained using datelife (gray).

File 40 Name: Sanchez-Reyes_etal_2022_supplementary_figure_S15.tre    
File 40 Description: Newick file of chronogram obtained with datelife, shown in supplementary Figure S15 (gray).

File 41 Name: Sanchez-Reyes_etal_2022_supplementary_figure_S16.jpg    
File 41 Description: JPG file of results of cross validation analysis of datelife's chronogram generating functions, using a tree topology from Price et al. 2014, chronogram 1. Comparison of original chronogram (black) and the chronogram obtained using datelife (gray).

File 42 Name: Sanchez-Reyes_etal_2022_supplementary_figure_S16.tre    
File 42 Description: Newick file of chronogram obtained with datelife, shown in supplementary Figure S16 (gray).

File 43 Name: Sanchez-Reyes_etal_2022_supplementary_figure_S17.jpg    
File 43 Description: JPG file of results of cross validation analysis of datelife's chronogram generating functions, using a tree topology from Price et al. 2014, chronogram 2. Comparison of original chronogram (black) and the chronogram obtained using datelife (gray).

File 44 Name: Sanchez-Reyes_etal_2022_supplementary_figure_S17.tre    
File 44 Description: Newick file of chronogram obtained with datelife, shown in supplementary Figure S17 (gray).

File 45 Name: Sanchez-Reyes_etal_2022_supplementary_figure_S18.jpg    
File 45 Description: JPG file of results of cross validation analysis of datelife's chronogram generating functions, using a tree topology from Roquet et al. 2014, chronogram 1. Comparison of original chronogram (black) and the chronogram obtained using datelife (gray).

File 46 Name: Sanchez-Reyes_etal_2022_supplementary_figure_S18.tre    
File 46 Description: Newick file of chronogram obtained with datelife, shown in supplementary Figure S18 (gray).

File 47 Name: Sanchez-Reyes_etal_2022_supplementary_figure_S19.jpg    
File 47 Description: JPG file of results of cross validation analysis of datelife's chronogram generating functions, using a tree topology from Roquet et al. 2014, chronogram 2. Comparison of original chronogram (black) and the chronogram obtained using datelife (gray).

File 48 Name: Sanchez-Reyes_etal_2022_supplementary_figure_S19.tre    
File 48 Description: Newick file of chronogram obtained with datelife, shown in supplementary Figure S19 (gray).

File 49 Name: Sanchez-Reyes_etal_2022_supplementary_figure_S20.jpg    
File 49 Description: JPG file of results of cross validation analysis of datelife's chronogram generating functions, using a tree topology from Uyeda et al. 2017. Comparison of original chronogram (black) and the chronogram obtained using datelife (gray).

File 50 Name: Sanchez-Reyes_etal_2022_supplementary_figure_S20.tre    
File 50 Description: Newick file of chronogram obtained with datelife, shown in supplementary Figure S20 (gray).
"
```

@@

writeLines(text = c(line0, 
                    line1,
                    line2,
                    line3,
                    line4), con = "../dryad/README_Sanchez-Reyes_etal_2022_data.txt")
```

>>>>

```{r}
line2.1 <- "DATA & FILE OVERVIEW

@@

File 12 Name: Sanchez-Reyes_etal_2022_supplementary_figure_S1.pdf    
File 12 Description: PDf file showing results of cross validation analysis of datelife's chronogram generating functions. 
"
```

```{r}
line2.2 <- c()
# short study references:
names_phylo_all <- c("Barker et al. 2013",  # 1
                      "Barker et al. 2015 - chronogram 1",  # 2
                      "Barker et al. 2015 - chronogram 2",  # 3
                      "Burns et al. 2014",  # 4
                      "Claramunt et al. 2015",  # 5
                      "Gibb et al. 2015", # 6
                      "Hedges et al. 2015 - chronogram 1",  # 7
                      "Hedges et al. 2015 - chronogram 2",  # 8
                      "Hooper et al. 2017",  # 9
                      "Jetz et al. 2012 - chronogram 1",  # 10
                      "Jetz et al. 2012 - chronogram 2",  # 11
                      "Kimball et al. 2019 - chronogram 1", # 12
                      "Kimball et al. 2019 - chronogram 2", # 13
                      "Oliveros et al. 2019", # 14
                      "Price et al. 2014 - chronogram 1", # 15
                      "Price et al. 2014 - chronogram 2", # 16
                      "Roquet et al. 2014 - chronogram 1", # 17
                      "Roquet et al. 2014 - chronogram 2", # 18 
                      "Uyeda et al 2017")
file_index <- 12
fig_index <- 1
for (name in names_phylo_all) {
  file_index <- file_index + 1
  fig_index <- fig_index + 1
  x1 <- paste0("File ", file_index, " Name: Sanchez-Reyes_etal_2022_supplementary_figure_S", fig_index, ".jpg")
  x2 <- paste0("File ", file_index, " Description: JPG file of results of cross validation analysis of datelife chronogram generating functions, using a tree topology from ", name, ". Comparison of original chronogram (black) and the chronogram obtained using datelife (gray).\n")
  file_index <- file_index + 1
  x3 <- paste0("File ", file_index, " Name: Sanchez-Reyes_etal_2022_supplementary_figure_S", fig_index, "_cross_validated.tre")
  x4 <- paste0("File ", file_index, " Description: Newick file of chronogram cross validated using dates obtained with datelife, shown in gray on supplementary figure Sanchez-Reyes_etal_2022_supplementary_figure_S", fig_index, ".jpg\n")
  file_index <- file_index + 1
  x5 <- paste0("File ", file_index, " Name: Sanchez-Reyes_etal_2022_supplementary_figure_S", fig_index, "_source.tre")
  x6 <- paste0("File ", file_index, " Description: Newick file of source chronogram from", name, " used for the cross validaton analysis shown on supplementary figure Sanchez-Reyes_etal_2022_supplementary_figure_S", fig_index, ".jpg\n")

  line2.2 <- c(line2.2, x1, x2, x3, x4, x5, x6)
}

```

@@

writeLines(text = c(line0, 
                    line1,
                    line2.1,
                    line2.2,
                    line3,
                    line4), con = "../dryad/README_Sanchez-Reyes_etal_2022_data.txt")
```
